Manuscript simulations

### 2023-03-24 Manuscript simulations.Rmd
updated simulation summaries

```{r}

@@

```{r}
test <- one_sim(
  mat = compas_data[[1]][[1]]$Y,
  true_coords = compas_data[[1]][[1]]$true_coords,
  k = 2, 
  sim = 1, 
  niter = 100000,
  nchains = 3,
  nburnin = 50000,
  thin = 5,
  max_clus = 8,
  max_attempts = 10
)
```

>>>>

@@

```{r, eval = F}
test <- one_sim(
  mat = compas_data[[1]][[1]]$Y,
  true_coords = compas_data[[1]][[1]]$true_coords,
  k = 2, 
  sim = 1, 
  niter = 150000,
  nchains = 3,
  nburnin = 100000,
  thin = 5,
  max_clus = 8,
  max_attempts = 6
)
```

```{r}
# run sims
sim_tbl <- tibble(
  k = rep(2:5, each = 100),
  sim = rep(1:100, length(2:5))
)
run_sims <- function(sim_tbl, niter = 150000, nchains = 3, nburnin = 100000, thin = 5, max_clus = 8, max_attempts = 6){
  out <- list()
  for(i in 1:nrow(sim_tbl)){
    # grab sim params
    k_ <- sim_tbl$k[i]
    sim_ <- sim_tbl$sim[i]
    total_sim <- max(sim_tbl$sim) * (max(sim_tbl$k)-1)

    # message
    message(paste0("Beginning sim ", sim_, " of ", total_sim))

    # run one sim
    onerun <- one_sim(
      mat = compas_data[[k_-1]][[sim_]]$Y,
      true_coords = compas_data[[k_-1]][[sim_]]$true_coords,
      k = k_, 
      sim = sim_, 
      niter = niter,
      nchains = nchains,
      nburnin = nburnin,
      thin = thin,
      max_clus = max_clus,
      max_attempts = max_attempts
    )
    saveRDS(
      onerun, 
      paste0("simulations/agg_summaries/onerun_", k_, "_", sim_, ".rds")
    )
    out[[i]] <- onerun
  }
  return(out)
}
sims <- run_sims(
  sim_tbl,
  niter = 100000, 
  nchains = 3,
  nburnin = 50000, 
  thin = 5, 
  max_clus = 8, 
  max_attempts = 6
)
```

## Summarize K = 2

```{r}
clustering_list <- list()
ordination_list <- list()
onerun_files <- list.files("simulations/agg_summaries")
target_files <- onerun_files[grepl("onerun_2_", onerun_files)]
for(i in 1:length(target_files)){
  clustering_list[[i]] <- readRDS(paste0("simulations/agg_summaries/",target_files[i]))$clustering
  ordination_list[[i]] <- readRDS(paste0("simulations/agg_summaries/",target_files[i]))$ordination
}

# summarize clustering
clustering <- do.call("rbind", clustering_list)
sim_exclude <- clustering %>%
  group_by(sim) %>%
  summarize(sum_clus = sum(nclus)) %>%
  filter(is.na(sum_clus)) %>%
  dplyr::select(sim) %>% unlist %>% unname

clustering %>% 
  filter(sim %notin% sim_exclude) %>%
  group_by(method) %>%
  mutate(
    nclus_1 = ifelse(nclus == 1, 1, 0),
    nclus_2 = ifelse(nclus == 2, 1, 0),
    nclus_3 = ifelse(nclus == 3, 1, 0),
    nclus_4 = ifelse(nclus == 4, 1, 0),
    nclus_5 = ifelse(nclus == 5, 1, 0),
    nclus_6 = ifelse(nclus == 6, 1, 0),
    nclus_gr6 = ifelse(nclus > 6, 1, 0)
  ) %>%
  group_by(method) %>%
  summarize(
    nclus_1 = sum(nclus_1),
    nclus_2 = sum(nclus_2),
    nclus_3 = sum(nclus_3),
    nclus_4 = sum(nclus_4),
    nclus_5 = sum(nclus_5),
    nclus_6 = sum(nclus_6),
    nclus_gr6 = sum(nclus_gr6)
  )

clustering %>% 
  filter(sim %notin% sim_exclude) %>%
  group_by(method) %>%
  summarize(
    mean_pairwise = mean(pairwise_clus_prop)
  )

# summarize ordination
ordination <- do.call("rbind", ordination_list)
sim_exclude <- ordination %>%
  group_by(sim) %>%
  summarize(sum_procrustes = sum(procrustes_true)) %>%
  filter(is.na(sum_procrustes)) %>%
  dplyr::select(sim) %>% unlist %>% unname

ordination %>% 
  filter(sim %notin% sim_exclude) %>%
  group_by(method) %>%
  mutate(
    nclus_1 = ifelse(nclus == 1, 1, 0),
    nclus_2 = ifelse(nclus == 2, 1, 0),
    nclus_3 = ifelse(nclus == 3, 1, 0),
    nclus_4 = ifelse(nclus == 4, 1, 0),
    nclus_5 = ifelse(nclus == 5, 1, 0),
    nclus_6 = ifelse(nclus == 6, 1, 0),
    nclus_gr6 = ifelse(nclus > 6, 1, 0)
  ) %>%
  group_by(method) %>%
  summarize(
    nclus_1 = sum(nclus_1),
    nclus_2 = sum(nclus_2),
    nclus_3 = sum(nclus_3),
    nclus_4 = sum(nclus_4),
    nclus_5 = sum(nclus_5),
    nclus_6 = sum(nclus_6),
    nclus_gr6 = sum(nclus_gr6)
  )
